A Switching Planner for Combined Task and Observation Planning

### 2010-11-23 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/conc.tex
Relaxed conclusion

In this paper we address these challenges, developing a continual
planner that switches between sequential and decision-theoretic
planning. Given a POMDP model of the environment, sequential planning
is used to compute an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until a validation of an assumption about a runtime
proposition is requested.

The sequential mode of our system always schedules decision-theoretic
planning before executing actions that are not applicable with
certainty. This is vastly inefficient if the utility of that plan is
not dependent on the actions successful execution. This is the case
where a plan is conformant. Therefore, in the future we must develop a
cheap (heuristic) procedure to evaluate the utility of sensing at
steps in sequential plan.

>>>>

In this paper we address these challenges, developing a continual
planner that switches between fast sequential and expensive
decision-theoretic planning. Given a POMDP model of the environment,
sequential planning is used to compute an initial deterministic
sequential plan and complementary runtime evolution of the decision
process. That plan is executed until a validation of an assumption
about a runtime proposition is schedule. At that point a
decision-theoretic session performs some sensing which determines
whether or not the sequential session should be allowed to continue
without plan repair.

The sequential mode of our system always schedules decision-theoretic
planning before executing actions that are not applicable with
certainty. This is inefficient if the utility of the plan is not
dependent on that actions successful execution. This situation always
arises for conformant plans.
